Synthesizing by means of mice

### 2020-07-26 mice_synthesizing/Mice_Synthesizing.Rmd
Annotate code

# Use mice to impute all data

@@

## True results

@@

## Use mice to synthesize and to pool

### Pool the results of the synthetic datasets with the default mice settings.

@@

### Pool the results of the synthetic dataset with CART.

@@

### Results for both synthesization methods

@@

## Use mice to synthesize with pooling rules from Drechsler

@@

```{r}
mice_df <- data.frame(term = cart_fit$var, df = cart_fit$df)
syn_df <- data.frame(term = pooled$term, df = pooled$df)

@@

## Different synthesizing sequence

@@

# Bootstrap boys data

>>>>

# Introduction

@@

# Simulations

## Single dataset approach

### True results

@@

### Use mice to synthesize and to pool

#### Pool the results of the synthetic datasets with the default mice settings.

@@

#### Pool the results of the synthetic dataset with CART.

@@

#### Results for both synthesization methods

@@

### Use mice to synthesize with pooling rules from Drechsler

@@

```{r, fig.fullwidth = TRUE, dpi = 500}
mice_df <- data.frame(term = cart_fit$var, df = cart_fit$df)
syn_df <- data.frame(term = pooled$term, df = pooled$df)

@@

### Different synthesizing sequence

@@

## Bootstrapped boys data
